Let's talk about Thurstone \& Co.: An information-theoretical model for comparative judgments, and its statistical translation

### 2024-11-16 _tex/index.tex
Built site for gh-pages

Numerous studies have documented the effectiveness of CJ in assessing
traits and competencies over the past decade. These studies have
emphasized three aspects of the method's effectiveness: its reliability,
validity, and practical applicability. Research on reliability indicates
that CJ requires a relatively small number of pairwise comparisons
\citep{Verhavert_et_al_2019, Crompvoets_et_al_2022} to produce trait
scores that are as precise and consistent as those generated by other
assessment methods
\citep{Coertjens_et_al_2017, Goossens_et_al_2018, Bouwer_et_al_2023}.
Furthermore, evidence suggests that the reliability and time efficiency
of CJ are comparable, if not superior, to those of other assessment
methods when employing adaptive comparison algorithms
\citep{Pollitt_2012b, Verhavert_et_al_2022, Mikhailiuk_et_al_2021}. On
the other hand, research on validity suggests that scores generated by
CJ can accurately represent the traits under measurement
\citep{Whitehouse_2012, vanDaal_et_al_2016, Lesterhuis_2018, Bartholomew_et_al_2018, Bouwer_et_al_2023}.
Finally, research on practical applicability highlights the method's
versatility across both educational and non-educational contexts
\citep{Jones_2015, Bartholomew_et_al_2018, Jones_et_al_2019, Marshall_et_al_2020, Bartholomew_et_al_2020, Boonen_et_al_2020}.

@@

{The \emph{zero correlation between stimuli} represents two additional
assumtions about the method:}

>>>>

Numerous studies have documented the effectiveness of CJ in assessing
traits and competencies over the past decade. These studies have
emphasized three aspects of the method's effectiveness: its reliability,
validity, and practical applicability. Research on reliability indicates
that CJ requires a relatively small number of pairwise comparisons
\citep{Verhavert_et_al_2019, Crompvoets_et_al_2022} to produce trait
scores that are as precise and consistent as those generated by other
assessment methods
\citep{Coertjens_et_al_2017, Goossens_et_al_2018, Bouwer_et_al_2023}.
Furthermore, evidence suggests that the reliability and time efficiency
of CJ are comparable, if not superior, to those of other assessment
methods when employing adaptive comparison algorithms
\citep{Pollitt_2012b, Verhavert_et_al_2022, Mikhailiuk_et_al_2021}. On
the other hand, research on validity suggests that scores generated by
CJ can accurately represent the traits under measurement
\citep{Whitehouse_2012, vanDaal_et_al_2016, Lesterhuis_2018, Bartholomew_et_al_2018, Bouwer_et_al_2023}.
Finally, research on practical applicability highlights the method's
versatility across both educational and non-educational contexts
\citep{Kimbell_2012, Jones_et_al_2015, Bartholomew_et_al_2018, Jones_et_al_2019, Marshall_et_al_2020, Bartholomew_et_al_2020, Boonen_et_al_2020}.

@@

{The \emph{zero correlation between stimuli} represents two additional
assumptions about the method:}
